White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-12-06 papers/wdmerger_II/paper.tex
Add cite to Seitenzahl 2009

The upshot of this discussion is that the only way to resolve the
question is with higher resolution simulations. The semi-analytic
criterion provided by \cite{garg:2017} indicates that typical critical
radii for detonation of equal C/O material are in the range 1-10 km.
So, as pointed out by \citeauthor{kushnir:2013}, this numerical
stability issue is mainly a concern for simulations with
resolution of O(10 km) or worse. Detonations observed at higher
resolution are physically plausible because the critical temperature
gradient will be resolved. The high resolution needs to be achieved
with some combination of high resolution of the collision process
itself, and perhaps AMR based on the stability criterion as described
above, where we tag for refinement all zones above some $f_{s}$, the
ratio of the sound crossing time to the energy injection time. It
cannot be solely based on the burning stability criterion for the reason
described above, that a detonation may be spuriously locked in by
the low resolution regardless of how much resolution we add to it.

>>>>

The upshot of this discussion is that the only way to resolve the
question is with higher resolution simulations. The semi-analytic
criterion provided by \cite{garg:2017}, and the numerical calculations
of \cite{seitenzahl:2009}, give critical radii for spontaneous detonation.
For the densities we are interested in ($\sim 10^7\ \text{g / cm}^3$),
assuming equal C/O material, the critical radii are in the range 1-10 km.
So, as pointed out by \citeauthor{kushnir:2013}, this numerical
stability issue is mainly a concern for simulations with
resolution of O(10 km) or worse. Detonations observed at higher
resolution are physically plausible because the critical temperature
gradient will be resolved. The high resolution needs to be achieved
with some combination of high resolution of the collision process
itself, and perhaps AMR based on the stability criterion as described
above, where we tag for refinement all zones above some $f_{s}$, the
ratio of the sound crossing time to the energy injection time. It
cannot be solely based on the burning stability criterion for the reason
described above, that a detonation may be spuriously locked in by
the low resolution regardless of how much resolution we add to it.
